Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-12 apples_and_oranges.qmd
Tried adding a key column

# Step 2: turn dataframes to long
# A: turn long the rows with active
active_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
  rename(treatment = descr_active) %>% 
  rename_with(~ str_remove(., "_active")) %>% 
  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

control_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 
  rename(treatment = descr_control) %>% 
  rename_with(~ str_remove(., "_control")) %>% 
  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

>>>>

# Here I am creating a new column for df_long_for_metan, to be able to identify which studies featured a condition of interest. 
# for CBT, fluox, esc
cbt_fluox_esc_study_ids <- df_with_distinct_instruments %>%
  filter(active_type %in% c("cbt", "Fluoxetine", "Escitalopram")) %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key1 = ifelse(new_study_id %in% cbt_fluox_esc_study_ids, 1, NA))

# for wl 
wl_study_ids <- df_with_distinct_instruments %>%
  filter(control_type == "wl") %>%
  pull(new_study_id)
df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key2 = ifelse(new_study_id %in% wl_study_ids, 2, NA))

df_with_distinct_instruments <- df_with_distinct_instruments %>%
  mutate(key = paste(key1, key2, sep = "_"))

# Step 2: turn dataframes to long
# A: turn long the rows with active
active_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, key, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
  rename(treatment = descr_active) %>% 
  rename_with(~ str_remove(., "_active")) %>% 
  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)

control_df <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, key, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 
  rename(treatment = descr_control) %>% 
  rename_with(~ str_remove(., "_control")) %>% 
  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
  group_by(new_study_id) %>% #go through each study id and remove duplicates
  distinct(treatment, .keep_all = TRUE)
